GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-09-23 paper/kbanotebook2013/content/discussion.tex
added some formatting changes to make the file easier to edit

For slot extraction part, in order to improve the performance, what we need to are: 1) Using multi-class classifiers instead of pattern matching method to extract slot values in order to increase both recall and accuracy for slots “Affiliate”, “AssociateOf”, “FounderOf”, “EmployeeOf”, “FoundedBy” “TopMembers”, “Contact\_Meet\_Entity” and so on. 2) For special slots, like “Titles”, “DateOfDeath”, “CauseOfDeath”, “AwardsWon”, using different kind of advanced methods, e.g. classifiers, matching methods. 3) Using other NLP tools or using classifiers to overcome the drawbacks of the LingPipe’s inaccurate tags. The first and second tasks are the most important tasks we need to do.

>>>>

For slot extraction part, in order to improve the performance, what we need to 
are: 1) Using multi-class classifiers instead of pattern matching method to 
extract slot values in order to increase both recall and accuracy for slots
``Affiliate'', ``AssociateOf'', ``FounderOf'', ``EmployeeOf'', ``FoundedBy'',
``TopMembers'', ``Contact\_Meet\_Entity'' and so on. 2) For special slots, 
like “Titles”, “DateOfDeath”, “CauseOfDeath”, “AwardsWon”, using different 
kind of advanced methods, e.g.\ classifiers, matching methods. 3) Using other 
NLP tools or using classifiers to overcome the drawbacks of the LingPipe’s 
inaccurate tags. The first and second tasks are the most important tasks we 
need to do.

### 2013-09-23 paper/kbanotebook2013/content/implementation.tex
added some formatting changes to make the file easier to edit

We extract aliases for entities from wikipedia automatically both using API and using the actual page content, then apply pattern matching rules for slot value extraction.

@@

The format of the patterns is consist of five fields: 1) the type of the entity. 2) the slot name. 3) the pattern content. 4) the direction of the slot valule to the entity. 5) the type of the slot values. When we match one pattern, we match all the fields except the third field. The type of slot values could be the entity type tagged by Linpipe, noun phrase tagged by OpenNLP and the time phrases we hard-code. For these three kinds of patterns, we implement them in different ways accordingly.

Next we will explain the patterns with more details. Lets’s first look at one example of the first kind of patterns. For slot FounderOf, we have this pattern: \textless PER, FounderOf, founder, right, ORG\textgreater. PER means that the entity we are finding slot values for is a PER entity; FounderOf means this is a pattern for FounderOf slot. founder is the ankor word we are trying to match in the sentence text; right means that we are going to the right part of the sentence to match the pattern and find the slot value; ORG means the slot value should be a ORG entity.

@@

For accuracy, we have found that there are three major kinds of errors: 1) wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched by the patterns. We solve the first problem by using the wikipedia or twitter information of the entities to get better alias names. And we use post-processing to reduce the second and third types of errors.

@@

The SSF output of many extractions is noisy. The data contains duplicates and incorrect extractions. We can define rules to sanitize the output only using the information present in the SSF file. The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy. . We define two classes of rules deduplication rules and inference rules.

@@

 New slots can be deduced from existing slots by defineing inference rules. For example, two slots for the task are "FounderOf" and "FoundedBy". A safe assumtion is these slot names are biconditional logical connectives with the entities and slot values. Therefore, we can express a rule "X FounderOf Y" equals "Y FoundedBy X" where X and Y are single unique entities. Additionally, we found that the slot names "Contact\_Meet\_PlaceTime" could be infered as "Contact\_Meet\_Entity" if the Entity was a FAC and the extracted sentence contained an additional ORG/FAC tag.

We also remove erronious slots that have extractions that are several pages in length or tool small. Errors of extracting long sentences can typically be attributed to poor sentence parsing of web documents. We have some valid "small" extractions. For example a comma may separate a name and a title (e.g. "John, Professor at MIT"). But such extraction rules can be particularly noisy, so we check to see if the extracted values have good entity values.

>>>>

We extract aliases for entities from Wikipedia automatically both using API 
and using the actual page content, then apply pattern matching rules for slot 
value extraction.

@@

The format of the patterns is consist of five fields:
1) the type of the entity. 
2) the slot name.
3) the pattern content.
4) the direction of the slot value to the entity.
5) the type of the slot values. When we match one pattern, we match all the 
fields except the third field. The type of slot values could be the entity 
type tagged by Lingpipe, noun phrase tagged by OpenNLP and the time phrases we 
hard-code. For these three kinds of patterns, we implement them in different 
ways accordingly.

Next we will explain the patterns with more details. Lets’s first look at one 
example of the first kind of patterns. For slot FounderOf, we have this
pattern: \textless PER, FounderOf, founder, right, ORG\textgreater. PER means 
that the entity we are finding slot values for is a PER entity; FounderOf 
means this is a pattern for FounderOf slot. Founder is the anchor word we are 
trying to match in the sentence text; right means that we are going to the 
right part of the sentence to match the pattern and find the slot value; ORG 
means the slot value should be a ORG entity.

@@

For accuracy, we have found that there are three major kinds of errors: 1) 
wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched 
by the patterns. We solve the first problem by using the wikipedia or twitter 
information of the entities to get better alias names. And we use
post- processing to reduce the second and third types of errors.

@@

The SSF output of many extractions is noisy. The data contains duplicates and 
incorrect extractions. We can define rules to sanitize the output only using 
the information present in the SSF file. The file is processed in time order, 
in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
two classes of rules deduplication rules and inference rules.

@@

 New slots can be deduced from existing slots by defineing inference rules. 
 For example, two slots for the task are "FounderOf" and "FoundedBy". A safe 
 assumtion is these slot names are biconditional logical connectives with the 
 entities and slot values. Therefore, we can express a rule "X FounderOf Y" 
 equals "Y FoundedBy X" where X and Y are single unique entities. Additionally,
 we found that the slot names "Contact\_Meet\_PlaceTime" could be infered as
 "Contact\_Meet\_Entity" if the Entity was a FAC and the extracted sentence 
 contained an additional ORG/FAC tag.  
We also remove erronious slots that have extractions that are several pages in 
length or tool small. Errors of extracting long sentences can typically be 
attributed to poor sentence parsing of web documents. We have some valid
"small" extractions. For example a comma may separate a name and a title
(e.g. "John, Professor at MIT"). But such extraction rules can be particularly 
noisy, so we check to see if the extracted values have good entity values.

### 2013-09-23 paper/kbanotebook2013/content/system.tex
added some formatting changes to make the file easier to edit

In this section we provide a high level description of the pipeline(system) design for big data analysis regarding TREC KBA the Stream Slot Filling (SSF) task. Our pipeline of processing the corpus consists of a two layer indexing system main section in our system regarding indexing the corpus, We started off by trying to use the off-the-shelf tools for this task. Mainly we started by using Scala/Spark\cite{ferc11} to benefit from the paralellization performance there.  Spark was not as efficient as expected and the overhead was much more than tolerable. We tried to use Scala parallelization itself to do the job, and unfortunately it did not satisfy our needs, there was excessive memory overhead on map reduce jobs. We migrated the core of the system to Java Parallelism APIs and that was not good enough either, we wanted better. So we built our own parallel system which in actual performance had the least of overhead, the least memory consumption and the most robust memory model which avoided unpredictable CPU stalls on garbage collections in processing the corpus. In what follows we will describe each step of this evolution in details. Figure \ref{fig:system} shows a schematic view of the system. The platform that we run our pipeline over was a 32 core server having 64GB of memory.

@@

Regarding Cumulative Citation Recommendation we perform exact string matching and treat all the documents that mention an entity equally likely to be citable. For future iterations of the paper we have ideas on how to score documents based on their likelihood of citation worthiness but for this iterations we treat all mentioning documents equally likely. One of the reasons for this is that in former TREC KBA reports \cite{JFrank12} there were observations of how non-mentioning documents have highly low chance of being citeable in wikipedia. So we take on that and ignore non-citing documents. Regarding mentioning but garbage, neutral or central documents we produce more slot values which can be later on filtered out in the high accuracy filter section.

>>>>

In this section we provide a high level description of the pipeline(system) 
design for big data analysis regarding TREC KBA the Stream Slot Filling (SSF) 
task. Our pipeline of processing the corpus consists of a two layer indexing 
system main section in our system regarding indexing the corpus, We started 
off by trying to use the off-the-shelf tools for this task. Mainly we started 
by using Scala/Spark\cite{ferc11} to benefit from the parallelization 
performance there.  Spark was not as efficient as expected and the overhead 
was much more than tolerable. We tried to use Scala parallelization itself to 
do the job, and unfortunately it did not satisfy our needs, there was 
excessive memory overhead on map reduce jobs. We migrated the core of the 
system to Java Parallelism APIs and that was not good enough either, we wanted 
better. So we built our own parallel system which in actual performance had 
the least of overhead, the least memory consumption and the most robust memory 
model which avoided unpredictable CPU stalls on garbage collections in 
processing the corpus. In what follows we will describe each step of this 
evolution in details. Figure~\ref{fig:system} shows a schematic view of the 
system. The platform that we run our pipeline over was a 32 core server having 
64GB of memory.

@@

Regarding Cumulative Citation Recommendation we perform exact string matching 
and treat all the documents that mention an entity equally likely to be citable.
For future iterations of the paper we have ideas on how to score documents 
based on their likelihood of citation worthiness but for this iterations we 
treat all mentioning documents equally likely. One of the reasons for this is 
that in former TREC KBA reports \cite{JFrank12} there were observations of how 
non-mentioning documents have highly low chance of being citable in Wikipedia.
So we take on that and ignore non-citing documents. Regarding mentioning but 
garbage, neutral or central documents we produce more slot values which can be 
later on filtered out in the high accuracy filter section.
